Efficient and Effective Metric Space Indexing for Complete Record Linkage

### 2017-11-20 paper.tex
Update on Overleaf.

These blocking techniques are heuristics, commonly requiring domain
knowledge, such as the choice of appropriate blocking or sorting keys.
Poor choices of blocking attributes result in records being inserted
into a wrong block and thus true matches being missed. As a result,
existing blocking techniques can lead to \emph{incomplete} linkage.
Conversely, many of the record pairs compared in a block turn out to be
pairs with low similarities, corresponding to non-matches, resulting in
\emph{inefficient} linkage.

Locality sensitive hashing (LSH), originally proposed to allow
efficient nearest-neighbor search in high-dimensional
spaces~\cite{Ind98}, has been employed in record linkage as a blocking
technique where attribute values are hashed multiple times, and
blocks are created from those records that share some hash values.
\emph{HARRA} is a record linkage approach based on Min-hash and LSH
which blocks, compares, and then merges linked records in an iterative
fashion, where merged records are re-hashed to improve overall linkage
quality. Steorts et al.~\cite{Steorts2014} recently evaluated two LSH
variations, with their main conclusion being that in order to get good
results LSH methods must be tuned to the particular datasets being
linked. This requires good quality ground truth data which may be
unavailable or very expensive to obtain.

>>>>

These blocking techniques are heuristics, commonly requiring domain
knowledge, such as the choice of appropriate blocking or sorting keys.
Poor choices of blocking attributes result in records being inserted
into inappropriate blocks, and thus true matches being missed. As a
result, such techniques can lead to \emph{incomplete} linkage.
Conversely, many of the record pairs compared in a block may turn
out to have low similarity, corresponding to non-matches, resulting in
\emph{inefficient} linkage.

Locality sensitive hashing (LSH), originally proposed to allow
efficient nearest-neighbor search in high-dimensional
spaces~\cite{Ind98}, has been employed in record linkage as an indexing
technique where attribute values are hashed multiple times, and
blocks are created from those records that share some hash values.
\emph{HARRA} [CITATION?] is a record linkage approach based on Min-hash
[CITATION?] and LSH
which blocks, compares, and then merges linked records in an iterative
fashion, where merged records are re-hashed to improve overall linkage
quality. Steorts et al.~\cite{Steorts2014} recently evaluated two LSH
variations, with their main conclusion being that in order to get good
results LSH methods must be tuned to the particular datasets being
linked. This requires good quality ground truth data which may be
unavailable or very expensive to obtain.
